Universal Anonymous Signatures

### 2022-05-18 prism-backend/research/gsac/model-gsac.tex
Minor edits and fixing typos.

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, anything about its signer. In anonymous credentials
(with selective disclosure), it requires that no adversary should learn anything
about the holder of a credential that has been successfully shown, beyond that
he owns a credential containing the revealed attributes. In both GS and AC, it
is also typically required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
picks two (honest) users (or credentials in the AC case), the game randomly
chooses one of them, and lets the adversary request challenge
signatures/presentations from it. The adversary wins if it succeeds in guessing
which was the chosen user/credential better than guessing at random. In group
signatures, the game must also restrict the adversary from opening challenge
signatures. In anonymous credentials, the game must further constraint the
adversary to pick credentials that have some common subset of attributes, and
to use that common subset to request the challenge presentations. Here, we need
to take into account both. Furthermore, a key difference with group signatures
is that the game requires the adversary to output credential identifiers, rather
than user identifiers. Specifically, this means that the adversary may actually
output two credentials that belong to the same user. Therefore, in some sense,
the anonymity we get is more general than that of group signatures, as in \GSAC,
like in anonymous credentials, the adversary may request signatures from
different credentials, but belonging to the same user. The formal
specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\cid_0,\cid_1,\status) \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
     b^* \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \GSAC schemes.}
  \label{fig:exp-gsac-anonb}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\dattrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,
    \dattrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
    \in \CRED \lor \dattrs \not\subseteq \attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

>>>>

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, anything about its signer. In anonymous credentials
(with selective disclosure), it requires that no adversary should learn anything
about the holder of a credential that has been successfully shown, beyond that
he owns a credential containing the revealed attributes. In both GS and AC, it
is also typically required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
requests signatures from one out of two challenge users/credentials, where the
one actually producing the signatures is defined by a bit $b$. The adversary
wins if it succeeds in guessing which was the chosen user/credential better than
guessing at random. In group signatures, the game must also restrict the
adversary from opening challenge
signatures. In anonymous credentials, the game must constraint the
adversary to pick credentials that have some common subset of attributes, and
to use that common subset to request the challenge presentations. Here, we need
to take into account both. Furthermore, a key difference with group signatures
is that the game requires the adversary to output credential identifiers, rather
than user identifiers. Specifically, this means that the adversary may actually
output two credentials that belong to the same user. Therefore, in some sense,
the anonymity we get is more general than that of group signatures, as in \GSAC,
like in anonymous credentials, the adversary may request signatures from
different credentials, but belonging to the same user. The formal
specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     b^* \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\gpk,\isk,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \GSAC schemes.}
  \label{fig:exp-gsac-anonb}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\dattrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,
    \dattrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
    \in \CRED \lor \dattrs \not\subseteq \attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

### 2022-05-18 prism-backend/research/gsac/model-uas.tex
Minor edits and fixing typos.

        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \yeval = \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
          \pcind \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg):
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          (\yeval,\csig_b) \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          (\yeval,\csig_{1-b}) \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\csig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\yeval,\\
          \hspace*{74pt}\cuid_{1-b},\csig_{1-b},\cscid_{1-b})
          \rbrace \\
          \pcreturn (\csig_b,\yeval)
        }

@@

        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
          \feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
          \pcreturn (\sig,\yeval) \\
        }

@@

\paragraph{Anonymity.} %
In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
in our notion of anonymity for \UAS,
in order to prevent trivial wins by the adversary, we have to restrict that the
signing evaluation function outputs the same value for both user-credentials
pairs. Very interestingly, since our opening functionality does not
(necessarily) output the identity of the signer, \uline{we can even allow the
  adversary to open challenge signatures, as long as they produce the same
  output}. Other than this, the overall approach is similar: as
in group signatures and anonymous credentials, the adversary picks two pairs of
honest users and credential sets. We also require the adversary to pick an
evaluation function and an opener (hence, an opening function). Then, the
user-credential pair defind by the value of $b$ (unknown to the adversary) is
used to program the \CHALb oracle. The formal specification of the anonymity
game is given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,
\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,
\WREG,\SIGN,\OPEN)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\cuid_0,\cscid_0,\cuid_1,\cscid_1,\feval,\status) \gets \adv^{\Oanonc}
     (\choose,\parm) \\
     \pcif \feval \notin \famfeval: \pcreturn \bot \\
     b^* \gets \adv^{\Oanong} (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

>>>>

        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \pcif \yeval = \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
          \pcind \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg):
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          (\yeval,\csig_b) \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          (\yeval,\csig_{1-b}) \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\csig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\yeval,\\
          \hspace*{74pt}\cuid_{1-b},\csig_{1-b},\cscid_{1-b})
          \rbrace \\
          \pcreturn (\csig_b,\yeval)
        }

@@

        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
          \feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
          \pcreturn (\sig,\yeval) \\
        }

@@

\paragraph{Anonymity.} %
In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
in our notion of anonymity for \UAS,
in order to prevent trivial wins by the adversary, we have to restrict that the
signing evaluation function outputs the same value for both user-credentials
pairs. Very interestingly, since our opening functionality does not
(necessarily) output the identity of the signer, \uline{we can even allow the
  adversary to open challenge signatures, as long as they produce the same
  output}. Other than this, the overall approach is similar: as
in group signatures and anonymous credentials, the adversary asks for challenge
signatures from either one of two honest users and credential sets -- bit $b$,
unkown to the adversary, defining which one is used. Note that the adversary
also has to pick a signature valuation function \feval, as well as an opener
(passed as arguments to the \SIGN and \CHALb oracles). The formal specification
of the anonymity game is given in \figref{fig:exp-uas-anonb}, where $\Oanon
\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$

\begin{figure}[htp!]
  \centering
  \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     b^* \gets \adv^{\Oanon} (\status,\parm) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}
